% rubber: set program xelatex

\documentclass[10pt, letterpaper,sans]{moderncv}

\usepackage{graphicx}
\usepackage{multibib}
\newcites{Pub,Workshop,Working}{{Peer Reviewed},{Workshop Papers}, {Working Papers}}

% moderncv themes
\moderncvtheme[blue]{casual}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, 

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% Configure AMS
\usepackage{amsmath}
\usepackage{amsfonts}

% verbatim
\usepackage{verbatim}

% adjust the page margins
\usepackage[scale=0.8]{geometry}
\recomputelengths                             % required when changes are made to page layout lengths

% personal data
\firstname{Fangjian}
\familyname{Guo}

% \address{Department of Computer Science, Duke University}{Durham, NC 27708}    % optional, remove the line if not wanted
\mobile{(919) 599-8219}                    % optional, remove the line if not wanted

\email{richardkwo@gmail.com}                      % optional, remove the line if not wanted
\homepage{richardkwo.net} 
\social[github]{richardkwo} 
\social[linkedin]{richardkwo}
 
\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page


% font style
\newcommand{\dia}{$ \diamond \  $}
\newcommand{\bf}[1]{\textbf{#1}}
\newcommand{\it}[1]{\textit{#1}}
% font style
\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle \vspace{-3em}
\section{Personal Information}
\cvline{Name}{Richard (Fangjian) Guo}
\cvline{Homepage}{richardkwo.net}
\cvline{Email}{guo@cs.duke.edu}
\cvline{Address}{Department of Computer Science, Duke University \newline LSRC Building D125, 308 Research Dr, Campus Box 90129, Durham NC 27708}
\section{Education}
\cventry{2013 -- present}{\bf{Duke University}, Durham, NC, USA}{}{}{}{2nd-year PhD student in machine learning, Department of Computer Science}
\cvline{}{Advisor: Katherine A.~Heller ~~~ Committee Members: David B.~Dunson, Ronald Parr}
\cvline{}{GPA: \bf{3.97}/4.00}
\cventry{2009 -- 2013}{\bf{University of Electronic Science and Technology of China}, Chengdu, P.R.China}{}{}{}{B.Eng. in computer science and technology, graduated with \textbf{highest distinction}}
\cvline{}{Advisor: Tao Zhou ~~ Thesis: \textit{A Statistical Analysis of Diverging Moments.}}
\cvline{}{GPA: \bf{3.89}/4.00  ~~~ Ranking: \textbf{1}/110}
\section{Research Interests}
\cvline{Modeling}{Bayesian latent variable models, Bayesian nonparameteric models for hierarchical and network structures, Stochastic processes, Graphical models, Natural Language Processing.}
\cvline{Inference}{Scalable Bayesian inference, MCMC, Belief propagation}
\cvline{Theory}{Connecting statistical physics and machine learning, especially in graphical models and stochastic processes.}
\cvline{Application}{Modeling, understanding and predicting human behaviors, especially the interplay among structure, dynamics and contents in social processes, e.g.~online/offline communications, social networking, tagging and rating. Discovering and quantifying predictive patterns with machine learning techniques and applying them to recommendation, advertising and information retrieval. Testing and quantifying sociological theories with statistical models and large-scale data.}
\section{Research Experience}
\cventry{\scriptsize{Nov~2014 -- present}}{\bf{An EM-BP Framework for Recommendation Systems}}{\newline advised by \it{Prof.~Henry Pfister}}{}{}{Duke University}
\cvline{}{\small{Developing efficient and accurate rating prediction algorithms via a combined scheme of expectation-maximization and belief propagation. It significantly reduces the ``cold-start'' problem by exploiting long-range correlations.}}
\cventry{\scriptsize{April~2014 -- Oct~2014}}{\bf{Modeling Influence in Conversations}}{\newline advised by \it{Prof.~Katherine Heller and Prof.~Hanna Wallach}}{}{}{Duke University}
\cvline{}{\small{People's language usage tend to drift towards to those influential speakers in a conversation, which is a phenomenon known as ``linguistic accommodation''. We discover the latent influence network by modeling the evolution of language usage over time. Our model finds interesting patterns underlying political science and movie subtitle data.}}
\cventry{\scriptsize{Dec~2013 -- Jan~2014}}{\bf{Modeling and Calibrating Ratings across Categories}}{\newline advised by \it{Prof. David Dunson}}{}{}{Duke University}
\cvline{}{\small{In online rating systems, users tend to rate items with different internal standards across categories. By modeling such categorical dependence, ratings can be calibrated accordingly to remove the unfair bias and increase the diversity of recommendation systems. We proposed a Bayesian probit model that is able to discover interesting genre-specific ``bias'' from movie rating data.}}
%\section{Academic Activities}
%\cventry{Dec 2014}{NIPS 2014 Workshop on Networks: From Graphs to Rich Data}{}{}{}{Montreal, Quebec, Canada.}
%\cventry{Oct 2014}{The 5th Annual Text as Data Workshop}{}{}{}{Kellogg School of Management, Northwestern University, Chicago.}
%\cventry{July 2012}{CCAST summer school on statistical physics and complex systems}{}{}{}{Institute of Theoretical Physics, Chinese Academy of Sciences, Beijing.}
\section{Graduate Coursework}
\cvline{}{Probability \& Measure Theory, Computer Vision, Graphical Models \& Inference, Machine Learning, Advanced Machine Learning, Stochastic Processes, Statistical Inference, Design \& Analysis of Algorithms}
\section{Teaching}
\cvline{Fall 2014}{TA \& Recitation, STA 561: Probabilistic Machine Learning (graduate)}
\cvline{Spring 2014}{TA, CPS 270: Introduction to Artificial Intelligence (undergraduate)}
\section{Honors and Awards}
\cventry{2013 -- 2015}{\bf{Duke Graduate Fellowship}}{}{}{}{}
\cventry{2012}{\bf{Outstanding Winner} in 2012 Interdisciplinary Contest in Modeling \small{(0.3\%)}}{}{}{}{}
\cvline{}{\small{\textsc{COMAP, sponsored by SIAM, NSA and INFORMS}}}
\cventry{2012}{\bf{Outstanding Student} of the University \small{(0.2\%)}}{}{}{}{\textsc{University of Electronic Science and Technology of China}}
\cventry{2009 -- 2011}{\bf{National Scholarship}}{}{}{}{\textsc{Ministry of Education of China}}
\section{Skills}
\cvdoubleitem{Programming}{C/C++, Python, MATLAB, R}{Language}{English (fluent), Chinese (native)}
\closesection{}                   % needed to renewcommands
\renewcommand{\listitemsymbol}{-} % change the symbol for lists

%  Publications from a BibTeX file

\section{Publications}
\nocitePub{aistat2015, physicaa}
\bibliographystylePub{plain}
\bibliographyPub{GuoPublications}

\nociteWorking{embp, ratingpaper, powerlaw}
\bibliographystyleWorking{plain}
\bibliographyWorking{GuoPublications}

\nociteWorkshop{textasdata2014}
\bibliographystyleWorkshop{plain}
\bibliographyWorkshop{GuoPublications}

\clearpage

\end{document}


%% end of file `template_en.tex'.



